Raft Distributed Consensus Algorithm over WebRTC (Web Real-Time Communication)

### 2015-09-16 research_class/paper.tex
Remove extra "because".
Add demonstrative pronoun for clarity.
I think it's clearer with "that". *shrug*

In the context of Raft over WebRTC, the slowdown of background page
timers means that whenever the leader node is residing on a page that
is in the background, the propagation of transaction log entries slows
down substantially. This also means that other nodes which are in the
foreground are more likely to have an election timeout timer fire and
they are more likely to become a leader because they will be able to
send and receive votes more quickly than nodes that are in the
background.  In this sense the problem is self-correcting because over
the long term because higher performing nodes more are likely to start
and win elections. This also indicates dynamic adjustment of timeout
values may be a fruitful area of further study.

>>>>

In the context of Raft over WebRTC, the slowdown of background page
timers means that whenever the leader node is residing on a page that
is in the background, the propagation of transaction log entries slows
down substantially. This also means that other nodes which are in the
foreground are more likely to have an election timeout timer fire and
they are more likely to become a leader because they will be able to
send and receive votes more quickly than nodes that are in the
background.  In this sense the problem is self-correcting over
the long term because higher performing nodes more are likely to start
and win elections. This also indicates that dynamic adjustment of timeout
values may be a fruitful area of further study.
